### 2021-07-08 rad-icfp-2021/complexity.tex
minor

In this section, we introduce a simple cost model on our language and show 
that our reverse-mode transformation satisfies a version of the cheap gradient principle (Theorem \ref{thm:complexity}).

>>>>

In this section, we introduce a simple cost model for our language and show 
that our reverse-mode transformation satisfies a version of the cheap gradient principle (Theorem \ref{thm:complexity}).
